Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-09-30 paper-2024-sac-marl-neighbouring-strategies.tex
init intro

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography} 
\nocite{*}

>>>>

In recent years, machine learning and deep learning methods have gained more and more interests. 
%
In particular, regarding Multi-Agents Systems and Robotics, \emph{Reinforcement Learning} showed promising results.

Single-Agent Reinforcement Learning (SARL) has been extensively studied and used in literature to solve tasks in a broad range 
  of applied scenarios~\cite{DBLP:journals/air/SinghKS22,DBLP:journals/artmed/CoronatoNPP20,DBLP:journals/comsur/LuongHGNWLK19}.

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}
